Reproducible Research in R: A tutorial on how to do the same thing more than once

### 2021-08-05 manuscript.Rmd

  This paper introduces `repro`; an R-package that guides researchers in the installation and use of the tools required for computational reproducibility.
  It includes a tutorial on how to make a research project reproducible with the aid of `repro`.
  Finally, it introduces novel applications of reproducibility tools for scientific research, notably it includes the preregistration of study plans as reproducible computer code.
  Since computer code describes study plans more precisely than prose, this circumvents the shortcomings of ambiguous preregistrations that give researchers undesired degrees of freedom.
  Reproducibility made convenient with automation has hence a wide range of applications to accelerate scientific progress.

@@

Scientists increasingly strive to make research data, materials, and analysis code openly available i.e. within the Open Science movement.
Sharing these types of digital research products has the potential to increase scientific efficiency by enabling researchers to learn from each other and reuse materials, and to increase scientific reliability by facilitating the review and replication of published research results.
To some extent these potential benefits are contingent on whether these digital research products are reproducible. 
Reproducibility can be defined as the ability of anyone to obtain identical results from the *same* data with the *same* computer code [see @Peikert2019 for details].
The credibility of empirical research results hingeson their objectivity.
Objectivity in this context means "in principle it [the research finding] can be tested and understood by anybody." [@popperLogicScientificDiscovery2002, p. 22][^popper].
Only something reproducible can be tested and understood by anyone.
Therefore, reproducibility has long been considered integral to empirical research.
Unfortunately, despite increasing commitment to open science practices and good will, many projects can not yet be reproduced by other research teams [@obels2020].
This is because making a research project with all code, data, and materials reproducible comes with a variety of challenges (multiple versions of code and data, copy-and-paste errors, missing software, ambiguous computation), and there is a dire need for reproducibility standards.
With the technological advancement, it is now possible to make all digital products related to a research project available so that a research project can be reproduced with minimal effort.

This tutorial is aimed at researchers who intend to ensure the reproducibility of a research project and are willing to make relevant code, data, and materials available, whether publicly or on request.
We pursue two aims.

First, we introduce the reader to a workflow that maximizes the potential reproducibility of a research project.

This workflow builds on several technical solutions originating in the software engineering community. 
We discuss how these solutions address four common threats to reproducibility [see @Peikert2019 for details] and how they form a coherent workflow.
We further demonstrate how the R package `repro` supports researchers in adopting this workflow.
Second, we discuss opportunities that the reproducible workflow affords to improve not only how research outputs are created and recreated, but also how research itself is conducted.
One such opportunity is a strictly reproducible and unambiguous form of preregistration [@NosekRevolution2018] that builds upon an implementation of this reproducible workflow, the so-called *preregistration as code* (PAC).
PAC involves preregistering the intended analysis code and the bulk of the manuscript as a dynamic document, including the Introduction, Methods, and Results sections.
The resulting dynamic document closely resembles the final manuscript, but temporarily uses simulated data to generate placeholder results (e.g. figures, tables and statistics).
Once the empirical data are analyzed, the Results are updated automatically, and the Discussion can be written.

@@

This tutorial therefore demonstrates how to make R-based research projects reproducible, while striking a balance between rigor and ease-of-use.
A rigorous standard increases the likelihood that a project will remain reproducible as long as possible.
An easy-to-use standard, on the other hand, is more likely to be adopted.
Our approach is to promote broad adoption of easy-to-use practices, i.e., a "low threshold", and ensure that these practices are compatible with more complex rigorous solutions, i.e., a "high ceiling".
As researchers become more proficient with the tools involved, they can thus improve the reproducibility of their work.
The first part of this tutorial outlines threats to reproducibility and how the here presented reproducibility standard addresses these threats.

@@

1.	**Multiple inconsistent versions of code, data, or both**; for example
  - the data set could have changed over time because outliers were removed at a later stage or an item was later recoded
  - the analysis code could have been modified during writing of a paper because a bug was removed at some point in time
It may then be unclear which version of code and data was used to produce some reported set of results.
2.	**Copy-and-paste errors**; for example, results are often manually copied from a statistical computing language into a text processor; if a given analysis is re-run and results are manually updated in the text processor, this may inadvertently lead to inconsistencies between the reported result and the reproduced result;
3.	**Undocumented or ambiguous order of code execution**; for example, with multiple data and code files, it may be unclear which scripts should be executed in what order;  or, some of the computational steps are documented (e.g., final analysis), but other steps were conducted manually without documentation (e.g., running a scripts/commands by hand; copy-pasting results from one program to another)
4.	**Ambiguous dependencies**; for example, a given analysis may depend on a specific version of a specific software package, or rely on software that might not be available on a different computer or no longer exist at all; or, a different version of the same software may produce different results.

@@

1. **Version control**
2. **Dynamic document generation**
3. **Dependency tracking**
4. **Software management**

The remainder of this section briefly explains why each of these four building blocks is needed and their role in ensuring reproducibility.

**Version control** prevents the ambiguity that arises when multiple versions of code and data are created in parallel during the development phase of a research project.
Version control allows a clear link between which results were generated by which version of code and data.
This is important for reproducibility because only if it is obvious which version of data and code produced which results they can be said to be reproducible.
We recommend using **Git** for version control, because of its widespread adoption in the R community.

Git tracks changes to all project-related files (e.g., materials, data, and code) over time.
At any stage, individual files or the entire project can be compared to, or reverted to, an earlier version.
A version-controlled project makes the loss of files unlikely and also supports remote collaboration.
Git is built around snapshots that represent the project state at a given point in time.
Those snapshots are called "commits" and work like a "save" action.
Changes to files are collected in a _commit_.
Ideally, each commit has a message that succinctly describes these changes.
It is good practice to make commits for concrete milestones, e.g., "Commented on Introduction", "Added SES as a covariate", "Address Reviewer 2's comment 3".
This makes it easier to revert specific changes than when multiple milestones are joined in one commit, e.g., "Changes made on 19/07/2021".
Each commit "knows" its ancestor, and they form a timeline together.
The entirety of commits (i.e. the version-controlled project) is called a repository.
In Git, specific snapshots of a repository can be tagged, such that one can clearly label which version of the project was used to create a preregistration, preprint, or final version of the manuscript as accepted by a journal.
Git has additional features beyond basic version control, such as branches to facilitate collaboration.
@vuorreCuratingResearchAssets2018 provide a more extensive treatment how Git functions and how to use Git for research.
@bryanExcuseMeYou2018 provides additional information on how to track R Markdown documents.
Collaborating via Git requires the repository to be uploaded somewhere.
We recommend GitHub to host Git repositories because of its popularity among R users.
GitHub has many tools that ease project management and collaboration, and these tools are valuable in scientists everyday work, but they are not central to achieving reproducibility.

@@

To summarize, the workflow by @Peikert2019 requires four components (see Figure \@ref(fig:schematic)), dynamic document generation (using R Markdown), version control (using Git), internal dependency management (using Make), and containerization (using Docker).    
While R Markdown and Git are well integrated into the R environment through R Studio, Make and Docker require a level of expertise that is often beyond the training of scholars outside the field of information technology, which can represent a considerable hurdle in the acceptance and implementation of the workflow.
To remove this hurdle, we have developed the R package `repro` that supports scholars in setting up, maintaining, and reproducing research projects in R.
Importantly, a reproducible research project created with `repro` does not have the `repro` package itself as a dependency.
These projects will remain reproducible irrespective of whether `repro` remains accessible in future.
Users do not have to have repro installed to reproduce a project;
in fact, they do not even need to have R installed because the entire project can be rebuilt inside of a container that has R installed.
In the remainder, we will walk you through the creation of a reproducible research project with the package `repro`.

@@

This information makes explicitly declares the project's dependencies on files and R packages.
`repro` uses this information to construct a Makefile for the dependencies on other files and a Dockerfile that includes all required packages.
These two files together form the basis for consistency within a research project and consistency across different systems.
The function `repro::automate()` converts the metadata from all R Markdown files in the project (all files with the ending `.Rmd`) to a Makefile and a Dockerfile.
Together, these files allow users (including your future self) to reproduce every step in the analysis automatically.
It is important to re-run `repro::automate()` whenever you change the `repro`-metadata, change the output format, or add a new R Markdown file to the project, to keep the Makefile and Dockerfile up to date.
There is no harm in running it too often.
Other than the Makefile and the Dockerfile, which are created in the document root path, repro generates a few more files in the `.repro` directory (which we will explain in detail later), all of which you should add and commit to Git.

@@

Defining the research questions and planning data analysis before observing the research outcomes is referred to as *preregistration* [@NosekRevolution2018].
Preregistration increases the credibility of empirical results by separating a-priori planned and theory-driven analyses from those conducted unplanned and post-hoc, that is, after having seen the data.
Preregistration seeks to reduce "researcher degrees of freedom" [@NosekRevolution2018] in the execution of a planned study by limiting the number of decisions to be made after data has been collected, which could influence the results.
Preregistrations, however, have several shortcomings.
One shortcoming is that written study plans are often multi-interpretable and often do not achieve the level of unambiguity that are required to effectively zero the researcher degrees of freedom.
Even when several researchers describe their analysis with the same terms, use the same data, and investigate the same hypothesis, the results vary considerably [@silberzahnManyAnalystsOne2018].
The current best practice to ensure that the preregistration are comprehensive and specific enough is to use preregistration templates [like @bowmanOSFPreregTemplate2020].
These templates seek to improve the specificity of study plans by imposing structure [@bakkerEnsuringQualitySpecificity2020].
However, templates cannot remove researchers degrees of freedoms completely, because it is impossible to verbally describe every detail of an analysis for all but the most straightforward analysis.
A second limitation is that, just like primary research, preregistrations are susceptible to non-reproducibility.
To illustrate, a review of 210 preregistrations found that, even though 174 (67%) included a formal power analysis, only 34 (20%) of these could be reproduced [@bakkerRecommendationsPreregistrationsInternal2020].
Even when researchers have gone to great length in preregistering an analysis script,
they sometimes inexplicably fail to reproduce their own results.
For example, @steegenMeasuringCrowdAgain2014 realized after publication that part of their preregistered code results in different test statistic than they reported initially (see Footnote 7).
A final limitation is that written plans may turn out to be unfeasible once data are obtained and analyzed.
For example, a verbal description of a statistical model may be unidentified, e.g. if it includes reciprocal paths between variables, or more parameters than observed data.
Conversely, a model may be mis-specified in a major way; for example by omitting direct effects when the research question is about mediation, thus leading to a model with unacceptable fit.
Many researchers would only realize that such a model cannot be estimated once the data are obtained, thus necessitating a deviation from the preregistered plans.

The workflow described in this paper facilitates a rigorous and innovative solution to this problem:
Instead of describing the analysis in prose, researchers include the code required to conduct the analysis in the preregistration.
We term this approach of writing and publishing code at the preregistration stage *preregistration as code (PAC)*.
PAC has the potential to eliminate researchers degrees of freedom to a much greater extent than, e.g., preregistration templates.
Moreover, it removes the necessity to write two separate documents: A preregistration, and a manuscript.
For a PAC, researchers can write a reproducible, dynamically generated draft of their intended manuscript at the preregistration stage.
This includes the Introduction, Methods, and Results sections.
These results are initially based on simulated data with the same structure as the data they expect to obtain from their experiments.
For guidance on how to simulate data, see [@ref].
Once the preregistration is submitted and real data have been collected or made available,
the document can be reproduced with a single command, thus updating the Results to their final version.

@@

A single simulated dataset already helps to ensure that the plan is viable under certain circumstances.
However, repeated simulation with varying parameters, a so-called Monte Carlo simulation, lets researchers play through several scenarios.
Monte Carlo simulation lets researchers navigate several trade-offs regarding their resources.
In the simplest case, they can assess the power (the probability to detect an effect of a given size) for varying numbers of observations in the simulation to determine the required sample size for their study [@brandmaier2018precision].
@bakkerRecommendationsPreregistrationsInternal2020 found that a formal power analysis does not necessarily increase the planned sample size.
Researchers may also evaluate how the data analysis copes with expected data complications, e.g. non-normal data [@harrisonIntroductionMonteCarlo2010; @raychaudhuriIntroductionMonteCarlo2008].

@@

To write a PAC, researchers should start by drafting a manuscript in the form of an R Markdown.
When they have completed the method section, they should begin writing code.
We suggest writing three functions for each planned hypothesis, one for the planned analysis, one for simulating the data and one for reporting the results.
At the heart of a PAC lies the planned analysis, so researchers should first draft a function called `planned_analysis()` that fits the description in their method section.
This function should receive the data and derive relevant results from it.

@@

We argued that PAC has several advantages over classical preregistration and have outlined how to implement it.
To illustrate how PAC works in practice and help researchers implementing PAC themselves, we have conducted a PAC that serves as a guiding example.
We will use an exemplary research question that was based on openly available data and merely chosen for simplicity of illustration:

@@

We then translated this methods section into the following `planned_analysis()` function:

@@

This paper demonstrated how the R package `repro` supports researchers in creating reproducible repositories and reproducible manuscripts.
These are important building blocks for transparent and cumulative science because they enable others to reproduce statistical and computational results and reports later in time and on different computers.
The workflow we present here rests on four software solutions, version control, dynamic document generation, dependency tracking and software management to all but guarantee reproducibility.
We first demonstrated how to create a reproducible research project.
Then, we illustrated how such a project can be reproduced - either by the original author and/or collaborators, or by a third party.
We finally presented an example of how the rigorous and automated reproducibility workflow introduced by `repro` may enable other innovations,
such as the preregistration as code (PAC).
A PAC incorporates all planned analysis code into a reproducible manuscript that already renders the expected results.
These results are based on simulated data, so that there is no danger of peeking at the real data while writing the scripts.
The entire manuscript, including planned analyses, is preregistered.
This way, all researcher's degrees of freedom are eliminated.
Once real data is gathered, the reproducible manuscript is (re-)created with the real data.
Because the same dynamic document serves as preregistration and final manuscript, researcher, reviewers and editors only have to revise one document.
To editors, reviewers and readers it is obvious how the researchers deviated from the preregistration because everything is under version control.
The likelihood of those deviations, while unavoidable, is decreased by using simulated data to verify the suitability of the analysis plan.
This analysis plan may contain data depended decisions to further decrease the likelihood that researcher are unable stick to their preregistration

@@

We realize that PACs are challenging.
Not every research question or project is suitable for preregistration in general, and many analytical strategies could prove unwieldy for a PAC.
Therefore, PAC should not be seen as an attempt to invalidate classical preregistration or not preregistered research but as a complement.
The rigidity of PAC is only than to much of a good thing, if one holds the view that researchers can for no reason deviate from their preregistration.
However, we are convinced that many reasons justify changing the preregistered code, but are equally convinced that readers should judge themselves if they find these deviations from the preregistration meaningful.
PAC enables just that.
Researcher can change their plans and possibly defend their decision, e.g. in the discussion, while readers of the manuscript can clearly see what was changed through version control.

Another challenge is that PAC requires more programming expertise than a usual analysis.
In contrast to a reproducible script, which should work on the same data, a PAC must work on different data.
We call the property of code that can run on different inputs from a similar context and produce valid outputs "reusability".
This property is based on reproducibility but requires the researcher to more carefully write the software [@lanerganSoftwareEngineeringReusable1989] such that it is _build-for-reuse_ [@al-badareenReusableSoftwareComponents2010].
The reproducible workflow we present here is heavily automated and hence promotes reusability.

>>>>

  This paper introduces `repro`, an R-package, which guides researchers in the installation and use of the tools required for making a research project reproducible.
  Finally, we suggest the use of the proposed tools for the preregistration of study plans as reproducible computer code (preregistration as code; PAC).
  Since computer code represents the planned analyses exactly as they will be executed, it is more precise than natural language descriptions of those analyses, which merely complement the PAC as a more readable summary. 
  PAC circumvents the shortcomings of ambiguous preregistrations that may give researchers undesired degrees of freedom.
  Hence, reproducibility made convenient with automation has a wide range of applications to accelerate scientific progress.

@@

Scientists increasingly strive to make research data, materials, and analysis code openly available.
Sharing these types of digital research products has the potential to increase scientific efficiency by enabling researchers to learn from each other and reuse materials, and to increase scientific reliability by facilitating the review and replication of published research results.
To some extent these potential benefits are contingent on whether these digital research products are reproducible. 
Reproducibility can be defined as the ability of anyone to obtain identical results from the *same* data with the *same* computer code [see @Peikert2019 for details].
The credibility of empirical research results hinges on their objectivity.
Objectivity in this context means "in principle it [the research finding] can be tested and understood by anybody." [@popperLogicScientificDiscovery2002, p. 22][^popper].
Only something reproducible can be tested and understood by anyone.
Therefore, reproducibility has long been considered integral to empirical research.
Unfortunately, despite increasing commitment to open science practices and good will, many projects can not yet be reproduced by other research teams [@obels2020].
This is because making a research project with all code, data, and materials reproducible comes with a variety of challenges (e.g., missing software or ambiguous documentation of all steps taken), and there is a dire need for reproducibility standards.
With the technological advancement, it is now possible to make all digital products related to a research project available so that a research project can be reproduced with minimal effort.

This tutorial is aimed at researchers who intend to ensure the reproducibility of a research project and are willing to make relevant code, data, and materials available, whether publicly or on request.
We pursue two aims. First, we introduce the reader to a workflow that maximizes the potential reproducibility of a research project. Second, we introduce a computational preregistration scheme based on reproducible research projects.

The proposed workflow builds on several technical solutions originating from software engineering. 
We discuss how these solutions address four common threats to reproducibility [see @Peikert2019 for details] and how they interact to form a coherent workflow.
We further demonstrate how the R package `repro` supports researchers in adopting this workflow.
Second, we discuss opportunities that the reproducible workflow affords to improve not only how research outputs are created and recreated, but also how research itself is conducted.
One such opportunity is a strictly reproducible and unambiguous form of preregistration [@NosekRevolution2018] that builds upon an implementation of this reproducible workflow, the so-called *preregistration as code* (PAC).
PAC involves preregistering the intended analysis code and the bulk of the manuscript as a dynamic document, including typical sections like Introduction, Methods, and Results.
The resulting dynamic document closely resembles the final manuscript, but temporarily uses simulated data to generate placeholder results (e.g. figures, tables and statistics).
With these placeholders, authors preregister the exact presentation of their results without having seen real data yet.
Once the empirical data are analyzed, the Results are then updated automatically, and the Discussion can be written to finalize the report.

@@

Therefore, this tutorial demonstrates how to make R-based research projects reproducible, while striking a balance between rigor and ease-of-use.
A rigorous standard increases the likelihood that a project will remain reproducible as long as possible.
An easy-to-use standard, on the other hand, is more likely to be adopted.
Our approach is to promote broad adoption of easy-to-use practices, i.e., a "low threshold", and ensure that these practices are compatible with more complex rigorous solutions, i.e., a "high ceiling".
As researchers become more proficient with the tools involved, they can thus improve the reproducibility of their work.

@@

1.	**Multiple inconsistent versions of code, data, or both**; for example, the data set could have changed over time because outliers were removed at a later stage or an item was later recoded; or, the analysis code could have been modified during writing of a paper because a bug was removed at some point in time
It may then be unclear which version of code and data was used to produce some reported set of results.
2.	**Copy-and-paste errors**; for example, results are often manually copied from a statistical computing language into a text processor; if a given analysis is re-run and results are manually updated in the text processor, this may inadvertently lead to inconsistencies between the reported result and the reproduced result;
3.	**Undocumented or ambiguous order of code execution**; for example, with multiple data and code files, it may be unclear which scripts should be executed in what order;  or, some of the computational steps are documented (e.g., final analysis), but other steps were conducted manually without documentation (e.g., executing a command manually instead of in a script; copy-pasting results from one program to another)
4.	**Ambiguous dependencies**; for example, a given analysis may depend on a specific version of a specific software package, or rely on software that might not be available on a different computer or no longer exist at all; or, a different version of the same software may produce different results.

@@

1. Version control
2. Dynamic document generation
3. Dependency tracking
4. Software management

The remainder of this section briefly explains why each of these four building blocks is needed and details their role in ensuring reproducibility.

**Version control** prevents the ambiguity that arises when multiple versions of code and data are created in parallel during the lifetime (and in particular, in the development phase) of a research project.
Version control allows a clear link between which results were generated by which version of code and data.
This is important for reproducibility because only if it is obvious which version of data and code produced which results they can be said to be reproducible.
We recommend using **Git** for version control, because of its widespread adoption in the R community.

Git tracks changes to all project-related files (e.g., materials, data, and code) over time.
At any stage, individual files or the entire project can be compared to, or reverted to, an earlier version.
A version-controlled project makes the loss of files unlikely and also supports remote collaboration.
Git is built around snapshots that represent the project state at a given point in time.
Those snapshots are called "commits" and work like a "save" action.
Changes to files are collected in a _commit_.
Ideally, each commit has a message that succinctly describes these changes.
It is good practice to make commits for concrete milestones (e.g., "Commented on Introduction", "Added SES as a covariate", "Address Reviewer 2's comment 3").
This makes it easier to revert specific changes than when multiple milestones are joined in one commit, e.g., "Changes made on 19/07/2021".
Each commit refers back to its ancestor, and they form a timeline together.
The entirety of commits (i.e. the version-controlled project) is called a repository.
In Git, specific snapshots of a repository can be tagged, such that one can clearly label which version of the project was used to create a preregistration, preprint, or final version of the manuscript as accepted by a journal.
Git has additional features beyond basic version control, such as branches to facilitate collaboration.
@vuorreCuratingResearchAssets2018 provide a more extensive treatment how Git functions and how to use Git for research.
@bryanExcuseMeYou2018 provides additional information on how to track R Markdown documents.
Collaborating via Git requires the repository to be uploaded somewhere.
We recommend GitHub to host Git repositories because of its popularity among R users.
GitHub has many tools that ease project management and collaboration, and these tools are valuable in scientists everyday work, but they are not central to achieving reproducibility.

@@

To summarize, the workflow by @Peikert2019 requires four components (see Figure \@ref(fig:schematic)), dynamic document generation (using R Markdown), version control (using Git), internal dependency management (using Make), and containerization (using Docker).    
While R Markdown and Git are well integrated into the R environment through R Studio, Make and Docker require a level of expertise that is often beyond the training of scholars outside the field of information technology, which can represent a considerable obstacle to the acceptance and implementation of the workflow.
To remove this obstacle, we have developed the R package `repro` that supports scholars in setting up, maintaining, and reproducing research projects in R.
Importantly, a reproducible research project created with `repro` does not have the `repro` package itself as a dependency.
These projects will remain reproducible irrespective of whether `repro` remains accessible in future.
Users do not have to have repro installed to reproduce a project;
in fact, they do not even need to have R installed because the entire project can be rebuilt inside of a container that has R installed.
In the remainder, we will walk you through the creation of a reproducible research project with the package `repro`.

@@

This information makes explicit what dependencies (in form of files and R packages) a project relies on .
`repro` uses this information to construct a Makefile for the dependencies on other files and a Dockerfile that includes all required packages.
These two files together form the basis for consistency within a research project and consistency across different systems.
The function `repro::automate()` converts the metadata from all R Markdown files in the project (all files with the ending `.Rmd`) to a Makefile and a Dockerfile.
Together, these files allow users (including your future self) to reproduce every step in the analysis automatically.
It is important to re-run `repro::automate()` whenever you change the `repro`-metadata, change the output format, or add a new R Markdown file to the project, to keep the Makefile and Dockerfile up to date.
There is no harm in running it too often.
Other than the Makefile and the Dockerfile, which are created in the document root path, repro generates a few more files in the `.repro` directory (which we will explain in detail later), all of which you should add and commit to Git.

@@

Defining the research questions and planning data analysis before observing the research outcomes is referred to as *preregistration* [@NosekRevolution2018].
Preregistration increases the credibility of empirical results by separating a-priori planned and theory-driven analyses from those conducted unplanned and post-hoc, that is, after having seen the data.
Preregistration seeks to reduce "researcher degrees of freedom" [@NosekRevolution2018] in the execution of a planned study by limiting the number of decisions to be made after data has been collected, which could bias the reported results.
Preregistrations, however, have several shortcomings.
One shortcoming is that written study plans are often multi-interpretable and often do not achieve the level of unambiguity that are required to effectively zero the researcher degrees of freedom.
Even when several researchers describe their analysis with the same terms, use the same data, and investigate the same hypothesis, the results vary considerably [@silberzahnManyAnalystsOne2018].
The current best practice to ensure that the preregistration are comprehensive and specific enough is to use preregistration templates [like @bowmanOSFPreregTemplate2020].
These templates seek to improve the specificity of study plans by imposing structure [@bakkerEnsuringQualitySpecificity2020].
However, templates cannot remove researchers degrees of freedoms completely, because it is impossible to verbally describe every detail of an analysis for all but the most straightforward analysis.
A second limitation is that, just like primary research, preregistrations are susceptible to non-reproducibility.
To illustrate, a review of 210 preregistrations found that, even though 174 (67%) included a formal power analysis, only 34 (20%) of these could be reproduced [@bakkerRecommendationsPreregistrationsInternal2020].
Even when researchers have gone to great length in preregistering an analysis script,
they sometimes inexplicably fail to reproduce their own results.
For example, @steegenMeasuringCrowdAgain2014 realized after publication that part of their preregistered code results in different test statistic than they reported initially (see Footnote 7).
A final limitation is that written plans may turn out to be unfeasible once data are obtained and analyzed.
For example, a verbal description of a statistical model may be unidentified, e.g. if it includes reciprocal paths between variables, or more parameters than observed data.
Conversely, a model may be mis-specified in a major way; for example by omitting direct effects when the research question is about mediation, thus leading to a model with unacceptable fit.
Many researchers would only realize that such a model cannot be estimated once the data are obtained, thus necessitating a deviation from the preregistered plans.
Of course this approach is not failsafe and researchers could still encounter problems after gathering data (ie. empierical underidentification) in which case they still have to deviate from their preregistration.

The workflow described in this paper facilitates a rigorous solution to this problem:
Instead of describing the analysis in prose, researchers include the code required to conduct the analysis in the preregistration.
We term this approach of writing and publishing code at the preregistration stage *preregistration as code (PAC)*.
PAC has the potential to eliminate researchers degrees of freedom to a much greater extent than, e.g., preregistration templates.
Moreover, it removes the necessity to write two separate documents:
A preregistration *and* a manuscript.
For a PAC, researchers can write a reproducible, dynamically generated draft of their intended manuscript at the preregistration stage.
This already includes most typical sections, such as Introduction, Methods, and Results.
These results are initially based on simulated data with the same structure as the data they expect to obtain from their experiments.
For guidance on how to simulate data, see [@ref].
Once the preregistration is submitted and real data have been collected or made available,
the document can be reproduced with a single command, thus updating the Results to their final version.

@@

A single simulated dataset already helps to ensure that the plan is viable under certain circumstances.
However, repeated simulation with varying parameters, a so-called Monte Carlo simulation, lets researchers play through several scenarios.
Monte Carlo simulation lets researchers navigate several trade-offs regarding their resources.
In the simplest case, they can assess the power (the probability to detect an effect of a given size) for varying numbers of observations in the simulation to determine the required sample size for their study [@brandmaier2018precision].
@bakkerRecommendationsPreregistrationsInternal2020 found that a formal power analysis does not increase the planned sample size on avaerage but could help to invest resources more efficiently.
Researchers may also evaluate how the data analysis copes with expected data complications, e.g. non-normal data [@harrisonIntroductionMonteCarlo2010; @raychaudhuriIntroductionMonteCarlo2008].

@@

To write a PAC, researchers should start by drafting a manuscript in the form of an R Markdown.
When they have completed the method section, they should begin writing code.
We suggest writing three functions for each planned hypothesis, one for the planned analysis, one for simulating the data and one for reporting the results.
We capture these distinct tasks in the form of explicit R-functions but researcher may use any form (e.g. scripts) as long as it serves to simulate, analyze, and report.
The simulate and report function can of course be reused, if appropriate, across multiple hypotheses.
At the heart of a PAC lies the planned analysis, so researchers should first draft a function called `planned_analysis()` that fits the description in their method section.
This function should receive the data and derive relevant results from it.

@@

We argued that PAC has several advantages over classic preregistration and have outlined how to implement it.
To illustrate how PAC works in practice and help researchers implementing PAC themselves, we have conducted a PAC that serves as a guiding example.
We will use an exemplary research question that was based on openly available data and merely chosen for simplicity of illustration:

@@

The methods section is the translation of the following `planned_analysis()` function:

@@

This paper demonstrated how the R package `repro` supports researchers in creating reproducible research projects including reproducible manuscripts.
These are important building blocks for transparent and cumulative science because they enable others to reproduce statistical and computational results and reports later in time and on different computers.
The workflow we present here rests on four software solutions, version control, dynamic document generation, dependency tracking and software management to all but guarantee reproducibility.
We first demonstrated how to create a reproducible research project.
Then, we illustrated how such a project can be reproduced - either by the original author and/or collaborators, or by a third party.
We finally presented an example of how the rigorous and automated reproducibility workflow introduced by `repro` may enable other innovations,
such as the preregistration as code (PAC).
A PAC incorporates all planned analysis code into a reproducible manuscript that already renders the expected results.
These results are based on simulated data, so that there is no danger of peeking at the real data while writing the scripts.
The entire manuscript, including planned analyses, is preregistered.
This way, all researcher's degrees of freedom are eliminated.
Once real data is gathered, the reproducible manuscript is (re-)created with the real data.
Because the same dynamic document serves as preregistration and final manuscript, researcher, reviewers and editors only have to revise one document.
To editors, reviewers and readers it is obvious how the researchers deviated from the preregistration because everything is under version control.
The likelihood of those deviations, while never unavoidable, is decreased by using simulated data to verify the suitability of the proposed analysis plan.
This analysis plan may contain data-dependent decisions to increase flexibility of research plans.

@@

We realize that PACs are challenging.
Not every research question or project is suitable for preregistration in general, and many analytical strategies could prove impractical for a PAC.
Therefore, PAC should not be seen as an attempt to invalidate classical preregistration or not-preregistered research but as a complementary approach.
We are convinced that many reasons justify changing the preregistered code, but are equally convinced that readers should judge themselves if they find these deviations from the preregistration meaningful.
PAC enables just that.
Researcher can change their plans and possibly defend their decision, e.g. in the discussion, while readers of the manuscript can clearly see what was changed through version control.

Another challenge is that PAC requires more programming expertise than a usual analysis.
In contrast to a reproducible script, which should work on the same data, a PAC must work on different data of similar structure.
We call the property of code that can run on different inputs from a similar context and produce valid outputs "reusability".
This property is based on reproducibility but requires the researcher to more carefully write the software [@lanerganSoftwareEngineeringReusable1989] such that it is _build-for-reuse_ [@al-badareenReusableSoftwareComponents2010].
The reproducible workflow we present here is heavily automated and hence promotes reusability.
Furthermore, adhering to principles of reusability typically removes errors in the code and thus increases the likelihood that the statistical analysis is correct
